**Quantum Information Gravity: Proof of QIR Modifications to the Kerr Metric**

**Objective:** Derive the modifications to the Kerr metric induced by Quantum Information Gravity (QIR), incorporating entropy corrections and information-theoretic terms into the geometry of rotating black holes.

---

### **1. Statement of the Theorem**
We aim to modify the Kerr metric using QIR corrections. The standard Kerr metric in Boyer-Lindquist coordinates is given by:
\begin{equation}
    ds^2 = -\left( 1 - \frac{2GM}{\rho^2} \right) dt^2 + \frac{\rho^2}{\Delta} dr^2 + \rho^2 d\theta^2 + \left( r^2 + a^2 + \frac{2GM a^2}{\rho^2} \sin^2 \theta \right) d\phi^2 - \frac{4GM a}{\rho^2} \sin^2 \theta dt d\phi,
\end{equation}
where \( \rho^2 = r^2 + a^2 \cos^2 \theta \) and \( \Delta = r^2 - 2GM r + a^2 \).

Our goal is to introduce an additional term \( I_{\mu \nu} \), which represents the information correction, modifying spacetime curvature at quantum-information scales.

---

### **2. Mathematical Derivation**

#### **Step 1: Adding QIR Information Corrections**
We introduce a perturbation to the Kerr metric by modifying the mass term \( M \) with an information density function \( I(r) \):
\begin{equation}
    M_{\text{eff}} = M + \alpha I(r),
\end{equation}
where \( \alpha \) is a coupling constant that quantifies the strength of quantum information effects on spacetime.

Replacing \( M \) with \( M_{\text{eff}} \) in the Kerr metric, we obtain:
\begin{equation}
    ds^2_{\text{QIR}} = -\left( 1 - \frac{2G(M + \alpha I(r))}{\rho^2} \right) dt^2 + \frac{\rho^2}{\Delta} dr^2 + \rho^2 d\theta^2 + \left( r^2 + a^2 + \frac{2G(M + \alpha I(r)) a^2}{\rho^2} \sin^2 \theta \right) d\phi^2 - \frac{4G(M + \alpha I(r)) a}{\rho^2} \sin^2 \theta dt d\phi.
\end{equation}

---

### **3. Logical Justification**
- **Why This Matters:** The modified Kerr metric introduces a quantum information correction to rotating black holes, potentially explaining deviations in black hole shadows observed by the Event Horizon Telescope (EHT).
- **Testability:** Predicts measurable deviations in frame-dragging and ergosphere geometry that could be detected in astrophysical observations.
- **Relation to QIR:** Provides a concrete application of quantum information corrections to classical spacetimes, reinforcing QIR’s predictive power.

---

### **4. Next Steps**
- Compute geodesics in the modified metric to determine observational signatures.
- Compare with Kerr-Newman and alternative quantum-corrected black hole models.
- Develop numerical simulations to validate predictions in extreme rotational regimes.

**All findings are documented separately—no prior documents have been altered.**

